{


\newcounter{func}
\setcounter{func}{10}
\renewcommand{\labelitemi}{
	\ifnum \value{func}<10$/F 0\arabic{func} /$\addtocounter{func}{10}
	\else $/F \arabic{func} /$\addtocounter{func}{10}\fi
	}

\section{Functional requirements} 
	
	\subsection{Scheduler}
	
		\begin{itemize}
			\item Support of Master-Worker scheduling strategy
			\item First in first out strategy
			\item Last in first out strategy
			\item Shortest job first strategy
			\item Longest job first strategy 
			\item Support of multiple-queues parallel scheduling strategy
			\item Rule-based multiple-queues strategy
			\item Random multiple-queues strategy
			\item Task-stealing multiple-queues strategy
			\item Statistics-based multiple-queues strategy
			\item Receive command line parameters
			\item Initialize the MPI-World
			\item Become either scheduler or executer
			\item Call the scientific Code 
			\item Receive a new task from the scientific code
			\item Query statistics for a task at data mining
			\item Read data from the bookkeeping database
			\item Write data into the bookkeeping database
			\item Does bookkeeping
			\item Execute a task
			\item Initialize the scientific code
			\item Change the scheduling strategy
		\end{itemize}
	
	\subsection{database}
	
		\begin{itemize}
			\item Generate files after initialization of the scheduler.
			\item Files will be placed after computation as usable files for plotting.
		\end{itemize}
		
		\subsubsection{Data mining}
	
			\begin{itemize}
				\item Read data from a statistic database
				\item Write data into the statistic database
				\item Analyse data from statistic
				\item Make forecast for the task
				\item Store statistics for computations
			\end{itemize}
	
		\subsubsection{Queue database}
	
			\begin{itemize}
				\item Read-functions for the queue file.
				\item Write-functions for the queue file.
			\end{itemize}
		
		\subsubsection{Bookkeeping database}
	
			\begin{itemize}
				\item Write-function for the bookkeeping file.
			\end{itemize}
	
		\subsubsection{Statistics database}
	
			\begin{itemize}
				\item Possibility to load an already used statistic file.
				\item Read-/write-functions for the data mining module for the statistic file.
				\item Search-function for similar data in statistics.
				\item Duplication of files on too high amount of requests.
			\end{itemize}
	
	
	\subsection{Interface}
	
		\begin{itemize}
			\item The program must provide the run\_task interface
			\item Receive different task types
		\end{itemize}
		
		
	\subsection{Visualization}
	
		\begin{itemize}
			\item Export bookkeeping to .vtk format
			\item Export statistic to .vtk format
			\item ???Export scientific results to .vtk format??? 
			% use gnuplot ????
		\end{itemize}

}
